---
title: "Metaanalysis Exercise"
author: "Ismayil Ismayilov"
date: today
format:  
  html:
    theme: lumen
    toc: true
    toc_float: true
title-block-banner: true
execute:
  echo: fenced
---

```{r}
#| label = "setup",
#| include = FALSE
library(meta)
library(metafor)
library(dplyr)
library(readxl)
#setwd("")
```

## Metaanalysis of Children's toy preferences

Let's focus on female toys.

---


```{r}
data <- read_excel("data/metaanalysis_data.xlsx")
```

Description of the data we are given:

Neutral toys (1 = neutral toys included; 2 = neutral toys not included); Parent present (1 = absent; 2 = minimal interaction; 3 = moderate or full interaction); Setting = location of study (1 = home; 2 = laboratory; 3 = nursery); Country = gender inequality index, a measure of how gender egalitarian the country was at the time the study took place.

Note. Quality is assessed using Newcastle–Ottawa Quality Assessment Scale criteria adapted for this study. A star indicates that the study fulfilled this criterion; an X indicates that the study did not fulfil this criterion. Case definition adequate: clear justification for the gendered nature of a toy, for example, based on research. Representativeness of cases: recruitment of consecutive participants. Selection of controls: whether boys and girls were comparable in terms of social background. Parental opinion: whether parents’ views on gender were measured. Comparability of both groups: the toys were comparable (in size, shape, etc.) and if the boys and girls were comparable in age. Ascertainment of behaviour: Play behaviour was clearly defined. Same ascertainment method for both groups: The measurement of the outcome (time spent playing with toy) was clearly defined. Nonresponse rate: whether either nonuptake or dropout rates reported.

---

```{r}
load("data/madata.RData")
Meta_Analysis_Data[1:5,]
```

Overall effect size

```{r}
m <- metagen(TE=Mean_boys_play_female,
             seTE=SD_boys_play_female,
             data=data,
             studlab=paste(Study),
             comb.fixed = TRUE,
             comb.random = FALSE)
m
```


---

The Funnel Plot

```{r}
m %>% funnel()
```

The funnel is not symmetrical - most of the publications are in the right part of the funnel. Still, the funnel encompasses 25/27 of the publications. 

---

Methods and Quality Effect on Results
```{r}
m %>% metareg(`Case definition adequate` + `Representativeness of cases` + `Selection of controls` + `Parental opinion` + `Comparability of both groups` + `Ascertainment of behaviour` + `Same ascertainment method for both groups` + `Non‐response rate` + `NOS score`)


m %>% metareg(`Case definition adequate` +
                `Representativeness of cases`+
                `Selection of controls` +
                `Parental opinion` + 
                `Comparability of both groups` + 
                `Ascertainment of behaviour` +
                `Non‐response rate`)
```

From a p-value perspective, it appears that none of the quality/method variables are statistically significant. However, it is worth noting that these variables still have substantial coefficient values.


---

The gender of the author influences the results.
```{r}
m %>% metareg(`Female authors` + `Male authors`)
```

Based on the p-value perspective at a significance level of 5%, the gender of the authors does not appear to have an impact on the results. However, if we consider a higher significance level of 10%, we can observe a positive influence on the results when the number of female authors in the study is taken into account.
